---
title: "Occupation Trends over Time in AYA"
author: "Amanda(Tianyi) Liu"
date: "13/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height=5, fig.width=8.5,
                      warning=FALSE, message=FALSE, fig.align="center")
```

```{r load_packages}
library(tidyverse)
library(haven)
library(ggplot2)
library(scales)
library(kableExtra)
library(knitr)
library(magrittr)
library(epitools)
```

## Pre-processing

### Loading Data

```{r load_data}
setwd("/Users/tianyi/Desktop/CUMC/Practicum/rakai_occupation_trend/data")

dat <- read_dta("all_data_original_id_1_19.dta")
dat_part_cleaned <- read_dta("R1_R18_partcleaned_incidence_20190913.dta")

colors <- c("#8d96a3", "#edae49", "94bee3", "#5ec0b2", "#9fc96c", "#5ec0b2")
```

### Creating full dataset

Only rows from the `all_data_original_id_1_19.dta` dataset will be included in the full dataset.

```{r merge_data}
# `hivrslt`: 1 2 3 7 8 9
hivrslt_dat <- 
  dat_part_cleaned %>% 
  select(study_id, round, hivrslt) %>%
  drop_na(hivrslt)

comm_num_dat <- 
  dat_part_cleaned %>% 
  select(study_id, round, comm_num) %>%
  drop_na(comm_num)

# .y: dat_part_cleaned
# If conflict in data, use data from "all_data_original_id_1_19.dta"

dat_all <- 
  dat %>%
  left_join(hivrslt_dat, by = c("study_id" = "study_id", "round" = "round")) %>%
  mutate(hivrslt = ifelse(is.na(hivrslt.x), hivrslt.y, hivrslt.x)) %>%
  select(-hivrslt.x, -hivrslt.y)

dat_all <-
  dat_all %>%  
  left_join(comm_num_dat, by = c("study_id" = "study_id", "round" = "round")) %>%
  mutate(comm_num = ifelse(is.na(comm_num.x), comm_num.y, comm_num.x)) %>%
  select(-comm_num.x, -comm_num.y)

dat_all %>% relocate(study_id) %>% group_by(study_id)
```

**Check if all requested variables exist**
  
```{r filter_var}
vars <- c("occup1", "occup2", "occupat1", "occupat2", "occs", # outcome
          "female", "ageyrs", "conf_age", "conf_age_flow", # demographics
          "comm_num",
          "radio", "bicycle","car","motorcyc","latrine", # SES
          "electric", "floor", "othfloor", "roof", "walls",
          "everpreg", "pregnow", "livechild", "numchild", # pregnancy
          "evermarr", "currmarr", "polymar", "evermend", # marriage  
          "pabuseyr", "ppushyr", "pfistyr", "pkickyr", # domestic violence
          "pweapyr", "patknyr", "pothvyr",
          "vthrsxpy", "pfocsxpy", "othfsxpy", "othpvyrs",# violence
          "hivrslt",# hiv result
          "occupat11", "occupat21", "occup11", "occup21", "occups1", # partner occupation
          "educate", "educyrs", "school", "finsch", "pregsch", # education
          "movesch", "menasch", "harasch", "bullwsch", "paresch",
          "accomsch", "othsch", "spesch", "addtrain")

dat_all %>% select(all_of(vars))

# "occupat1", "occupat2", "occs",
# "conf_age", "conf_age_flow", visit
# "livechild", "numchild",
# "othpvyrs", "hivrslt",
# "occup11", "occup21", "occups1",
# "addtrain"
```


### Data Cleaning

1. Create `age` variable by merging information from `conf_age_flow`, `conf_age`, `ageyrs`

```{r}
# Prioritization: `conf_age_flow` -> `conf_age` -> `ageyrs`
dat_all <-
  dat_all %>% 
  mutate(age = ifelse(is.na(conf_age_flow), conf_age, conf_age_flow)) %>% 
  mutate(age = ifelse(is.na(age), ageyrs, age))
```

2. Filter by age (15-24 year-old respondents) and generate `age groups` variable (15-17, 18-19, 20-24)

```{r}
dat_all <- 
  dat_all %>%
  filter(15 <= age & age <= 24) %>%
  mutate(age_cat = cut(age, breaks = c(14.5, 17.5, 19.5, 24.5), labels = c(1, 2, 3))) %>%
  mutate(age_cat = labelled(age_cat, c("15-17" = 1, "18-19" = 2, "20-24" = 3)))
```

3. Generate `visit` variable

```{r}
dat_all <- 
  dat_all %>% 
  mutate(visit = str_sub(round, 2, -1)) %>%
  mutate(visit = as.numeric(visit))
```

4. Generate `time period` variable (R1-R9 and R10-R19)

````{r}
dat_all <-
  dat_all %>% 
  mutate(period = cut(visit, breaks = c(0.5, 9.5, 19.5), labels = c(1, 2))) %>%
  mutate(period = labelled(period, c("R1-R9" = 1, "R10-R19" = 2)))
```

5. Generate `area` variable

```{r}
comm_fishing <- c(23, 38, 370, 770, 771, 772, 773, 774, 51, 776)
area_fishing <- rep("fishing", length(comm_fishing))

comm_rural <- c(3, 6, 7, 8, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 25, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 44, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 65, 67, 68, 77, 81, 84, 89, 94, 95, 103, 106, 107, 108, 109, 120, 177, 183, 256, 391, 401, 451, 468, 602, 755, 760, 900, 901)
area_rural <- rep("rural", length(comm_rural))

comm_periurban <- c(1, 2, 4, 5, 9, 22, 24, 26, 40, 45, 46, 74, 754)
area_periurban <- rep("periurban", length(comm_periurban))

area <- data.frame("comm_num" = c(comm_fishing, comm_rural, comm_periurban),
                   "area" = c(area_fishing, area_rural, area_periurban))

dat_all <-
  dat_all %>%
  left_join(area)
```

6. Categorize occupations for respondents (based on R1-18 part cleaned data)

```{r}
# labelling occupations
occup_lab <- c("Agriculture for home use/barter" = 1,
               "Agriculture for selling" = 2,
               "Housework in your own home" = 3,
               "Housekeeper (for relative or employer)" = 4,
               "Home brewing" = 5,
               "Government/clerical/teaching" = 6,
               "Fishing" = 7,
               "Student" = 8,
               "Military/police" = 9,
               "Shopkeeper" = 10,
               "Trading/vending" =	11,
               "Bar worker or owner" = 12,
               "Trucker" =	13,
               "Unemployed" = 14,
               "Other" = 15,
               "No additional occupation" = 88,
               "Medical worker (non-government)" = 16,
               "Casual laborer" =  17,
               "Waitress/Waiter/restaurant owner" = 18,
               "Hair dresser/Salon owner" = 19,
               "Construction (brick maker, builder, porter, painter, roofing)" = 20,
               "Mechanic (automobiles, bicycles, electronics)" = 21,
               "Boda Boda" = 22,
               "Client/Sex worker" = 23,
               "Sports betting, Gambling machine, Ludo" = 24, 
               "Don't know" = 97,
               "Don't know" = 98,
               "No response" = 99)

dat_all$occup1 <- dat_all$occup1 %>% labelled(occup_lab)
dat_all$occup2 <- dat_all$occup2 %>% labelled(occup_lab)

# categorize occupation
occup1_cat <- dat_part_cleaned %>% select(occup1, occup1_cat) %>% unique() %>% arrange(occup1) %>% drop_na(occup1)
occup2_cat <- occup1_cat %>% rename(occup2 = occup1, occup2_cat = occup1_cat)

occup1_mob <- dat_part_cleaned %>% select(occup1, occup1_mob) %>% unique() %>% arrange(occup1) %>% drop_na(occup1)
occup2_mob <- occup1_mob %>% rename(occup2 = occup1, occup2_mob = occup1_mob)

dat_all <- 
  dat_all %>% 
  left_join(occup1_cat, by = ("occup1" = "occup1")) %>%
  left_join(occup1_mob, by = ("occup1" = "occup1"))

dat_all <- dat_all %>% 
  left_join(occup2_cat, by = ("occup2" = "occup2")) %>%
  left_join(occup2_mob, by = ("occup2" = "occup2"))
```

7. Recoding/labelling `hivrslt` variable

```{r}
# `hivrslt`: 1 2 3 7 8 9
hivrslt_lab <- c("Negative" = 1,
                 "Positive" = 2,
                 "Indeterminate" = 3,
                 "Don’t know/Don’t remember" = 7,
                 "NA" = 8,
                 "No Response" = 9)

dat_all$hivrslt <- dat_all$hivrslt %>% labelled(hivrslt_lab)
```

8. Creating `SES` variable

```{r}
setwd("/Users/tianyi/Desktop/CUMC/Practicum/rakai_occupation_trend/data")

## 1. Select data
dat_ses <- dat_all %>%
  select(study_id, visit, radio, bicycle, motorcyc, car, latrine, electric, roof, floor, walls)

## 2. Recode
dat_ses <- dat_ses %>% 
  mutate(radio_r = ifelse(radio == 1, 1,ifelse(radio %in% c(2,3,5), 0, NA)),
         bicycle_r = ifelse(bicycle == 1, 1,ifelse(bicycle %in% c(2,3,5), 0, NA)),
         car_r = ifelse(car == 1, 1,ifelse(car %in% c(2,3,5), 0, NA)),
         motorcyc_r = ifelse(motorcyc == 1, 1,ifelse(motorcyc %in% c(2,3,5), 0, NA)),
         latrine_r = ifelse(latrine == 1, 1,ifelse(latrine %in% c(2,3,5), 0, NA)),
         electric_r = ifelse(electric == 1, 1,ifelse(electric %in% c(2,3,5), 0, NA)),
         roof_r = ifelse(roof %in% c(1,3), 1,ifelse(roof %in% c(2,4,5), 0, NA)),
         floor_r = ifelse(floor %in% c(2,3), 1,ifelse(floor %in% c(1,5), 0, NA)),
         walls_r = ifelse(walls %in% c(3), 1,ifelse(walls %in% c(1,2,4,5), 0, NA)))

## 3. Calculate raw SES index
df_asset_data <- dat_ses %>% 
  select(study_id, visit, radio_r, bicycle_r, motorcyc_r, car_r, latrine_r, electric_r, roof_r, floor_r, walls_r) %>% 
  pivot_longer(cols = radio_r:walls_r, names_to = "variable", values_to = "status") %>%
  arrange(study_id, visit)

df_pca_overall <- readxl::read_xlsx("./PCA_weights.xlsx") %>%
  select(variable, Overall) %>%
  rename(score = Overall) 

df_merge_overall <- left_join(df_asset_data, df_pca_overall, by = 'variable') %>%
  arrange(study_id, visit) %>%
  mutate(SES = status * score) 

df_ovSES_data <- df_merge_overall %>%
  arrange(study_id, visit) %>% 
  group_by(study_id, visit) %>% 
  summarise(SES = sum(SES), na.rm = F) %>%
  ungroup()

df_SES_data <- left_join(df_ovSES_data, dat_ses, by = c('study_id', 'visit')) %>%
  mutate(SES = structure(SES, label = "raw SES score")) %>%
  arrange(study_id, visit) %>%
  select(-na.rm)

## 4. Create SES z-score and 4-level SES categorical variable
df_cut_overall <- readxl::read_xlsx("./SES_cutpoints.xlsx") %>%
  select(cutpoints, Overall) %>%
  pivot_wider(names_from = cutpoints, values_from = Overall) %>%
  rename(Q1_zovSES = Q1_stdSES, Q2_zovSES = Q2_stdSES, Q3_zovSES = Q3_stdSES)

df_SES_data <- df_SES_data %>%
  mutate(zovSES = structure((SES - df_cut_overall$mean_SES) / df_cut_overall$sd_SES, label = "Overall standardized SES"), 
         SEScat = case_when(zovSES <= df_cut_overall$Q1_zovSES ~ 0,
                            zovSES > df_cut_overall$Q1_zovSES & zovSES <= df_cut_overall$Q2_zovSES ~ 1,
                            zovSES > df_cut_overall$Q2_zovSES & zovSES <= df_cut_overall$Q3_zovSES ~ 2,
                            zovSES > df_cut_overall$Q3_zovSES ~ 3)) %>%
  #mutate(SEScat = structure(SEScat, label = "zovSES categories"))
  mutate(SEScat = structure(ordered(SEScat, labels = c("lowest", "low-middle", "high-middle", "highest")), label = "zovSES categories"))

## 5. Merge into large dataset
df_SES_data <- df_SES_data %>% select(study_id, visit, SES, SEScat)
dat_all <- dat_all %>% left_join(df_SES_data, by = c("study_id" = "study_id", "visit" = "visit"))
```


## Describe trends over time in AYA occupations

### Visualize general occupation trends

1. Top occupations for each community type

```{r}
top_occup_area <- 
  dat_all %>% 
  select (study_id, visit, area, occup1) %>%
  gather(key, occup, -study_id, -visit, -area) %>%
  as_factor() %>%
  mutate(dummy = "yes") %>%
  spread(occup, dummy) %>%
  gather(job, value,  -study_id, -visit, -area, -key) %>%
  drop_na() %>%
  group_by(area, job) %>%
  summarise_at(vars(value), funs(sum(.=="yes")))

top_occup_area %>% 
  filter(area == "fishing") %>%
  arrange(desc(value)) %>%
  top_n(n=5) %>%
  ggplot(aes(x=factor(job, unique(job)), y=value)) +
  geom_bar(stat="identity", fill="#94bee3", width=0.6) +
  geom_text(aes(label=value), vjust = -1, color = "grey") +
  scale_x_discrete(labels = wrap_format(20)) +
  labs(x='', y='', title = "Top 5 Occupations for Fishing Communities") +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

top_occup_area %>% 
  filter(area == "periurban") %>%
  arrange(desc(value)) %>%
  top_n(n=5) %>%
  ggplot(aes(x=factor(job, unique(job)), y=value)) +
  geom_bar(stat="identity", fill="#94bee3", width=0.6) +
  geom_text(aes(label=value), vjust = -1, color = "grey") +
  scale_x_discrete(labels = wrap_format(20)) +
  labs(x='', y='', title = "Top 5 Occupations for Periurban Communities") +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

top_occup_area %>% 
  filter(area == "rural") %>%
  arrange(desc(value)) %>%
  top_n(n=5) %>%
  ggplot(aes(x=factor(job, unique(job)), y=value, fill)) +
  geom_bar(stat="identity", fill="#94bee3", width=0.6) +
  geom_text(aes(label=value), vjust = -1, color = "grey") +
  scale_x_discrete(labels = wrap_format(20)) +
  labs(x='', y='', title = "Top 5 Occupations for Rural Communities") +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```

2. Top occupations for each gender
  
```{r}
top_occup_gender <- 
  dat_all %>% 
  select (study_id, visit, female, occup1) %>%
  gather(key, occup, -study_id, -visit, -female) %>%
  as_factor() %>%
  mutate(dummy = "yes") %>%
  spread(occup, dummy) %>%
  gather(job, value,  -study_id, -visit, -female, -key) %>%
  drop_na() %>%
  group_by(female, job) %>%
  summarise_at(vars(value), funs(sum(.=="yes")))

top_occup_gender %>% 
  filter(female == "Male") %>%
  arrange(desc(value)) %>%
  top_n(n=5) %>%
  ggplot(aes(x=factor(job, unique(job)), y=value)) +
  geom_bar(stat="identity", fill="#94bee3", width=0.6) +
  geom_text(aes(label=value), vjust = -1, color = "grey") +
  scale_x_discrete(labels = wrap_format(20)) +
  labs(x='', y='', title = "Top 5 Occupations for Male") +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

top_occup_gender %>% 
  filter(female == "Female") %>%
  arrange(desc(value)) %>%
  top_n(n=5) %>%
  ggplot(aes(x=factor(job, unique(job)), y=value)) +
  geom_bar(stat="identity", fill="#94bee3", width=0.6) +
  geom_text(aes(label=value), vjust = -1, color = "grey") +
  scale_x_discrete(labels = wrap_format(20)) +
  labs(x='', y='', title = "Top 5 Occupations for Female") +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5))
```

3. Top occupations for each age group

```{r}
top_occup_agecat <- 
  dat_all %>% 
  select (study_id, visit, female, age_cat, occup1) %>%
  gather(key, occup, -study_id, -visit, -age_cat, -female) %>%
  as_factor() %>%
  mutate(dummy = "yes") %>%
  spread(occup, dummy) %>%
  gather(job, value,  -study_id, -visit, -age_cat, -key, -female) %>%
  drop_na() %>%
  group_by(age_cat, job, female) %>%
  summarise_at(vars(value), funs(sum(.=="yes"))) %>%
  mutate(frequency = sum(value))
  
for (i in c("15-17", "18-19", "20-24")){
  p <- top_occup_agecat %>% 
    filter(age_cat == i) %>%
    arrange(desc(frequency)) %>%
    head(10) %>%
    ggplot(aes(x = factor(job, unique(job)), y = value, fill = female, label = value)) +
    geom_bar(stat = "identity")+
    geom_text(size = 3, position = position_stack(vjust = 0.5)) +
    scale_fill_manual(values=colors) +
    scale_x_discrete(labels = wrap_format(15)) +
    labs(x='', y='', title = paste("Top Occupations for Respondents Aged", i)) +
    theme_minimal() + 
    theme(plot.title = element_text(hjust = 0.5),
          legend.title = element_blank())
  print(p)
}
```

It can be observed from above analysis that the top occupations for AYA include `Student`, `Agriculture for home use/barter`, `Housework in your own home`, `Agriculture for selling`, `Government/clerical/teaching`, `Trading/Vending` and `Other` (in addition to one community-specific occupation `Fishing`). Therefore, following analysis will be mainly focused on these occupations.

### Trends over time in AYA occupations

1. Trend by `visit`
  
```{r}
# Student 8
# Agriculture for home use/barter 1
# Housework in your own home 3
# Agriculture for selling 2
# Government/clerical/teaching 6
# Trading/Vending 11
# Other 15
# Fishing 7

occup_list <- c("Student", 
                "Agriculture for home use/barter", 
                "Housework in your own home", 
                "Agriculture for selling", 
                "Government/clerical/teaching", 
                "Trading/vending", 
                "Other", 
                "Fishing")
```

```{r}
occup_trend_visit <- dat_all %>% 
  select(study_id, visit, area, female, age, age_cat, occup1, occup1_cat, occup1_mob) %>%
  filter(occup1 %in% c(1, 2, 3, 6, 7, 8, 11, 15)) %>% 
  group_by(occup1, visit, female) %>%
  count(occup1) %>%
  as_factor()

occup_trend_visit %>%
  drop_na(female) %>%
  group_by(occup1) %>%
  ggplot(aes(x=visit, y=n, group=factor(female), color=factor(female))) +
  geom_line() + geom_point() + facet_wrap(~occup1) +
  labs(x='Visit', y='Number of Respondents', title="Trend Over Time for Occupations", subtitle="by visit") +
  scale_color_manual(values = colors) +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
                          plot.subtitle = element_text(hjust = 0.5),
                          legend.title = element_blank())

# for (i in occup_list){
#   p <- occup_trend_visit %>%
#     filter(occup1 == i) %>%
#     drop_na(female) %>%
#     ggplot(aes(x=visit, y=n, group=factor(female), color=factor(female))) +
#     geom_line() + geom_point()+
#     labs(x='Visit', y='Number of Respondents', title = paste("Trend Over Time for", i), subtitle = "(by visit)") +
#     scale_color_manual(values = colors) +
#     theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
#                             plot.subtitle = element_text(hjust = 0.5),
#                             legend.title = element_blank())
#   print(p)
# }
```
  
2. Trend by `age`
  
```{r}
occup_trend_age <- dat_all %>% 
  select(study_id, visit, area, female, age, age_cat, occup1, occup1_cat, occup1_mob) %>%
  filter(occup1 %in% c(1, 2, 3, 6, 7, 8, 11, 15)) %>% 
  group_by(occup1, age, female) %>%
  count(occup1) %>%
  as_factor()

occup_trend_age %>%
  drop_na(female) %>%
  group_by(occup1) %>%
  ggplot(aes(x=age, y=n, group=factor(female), color=factor(female))) +
  geom_line() + geom_point() + facet_wrap(~occup1) +
  labs(x='Age', y='Number of Respondents', title="Trend Over Time for Occupations", subtitle="(by age)") +
  scale_color_manual(values = colors) +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
                          plot.subtitle = element_text(hjust = 0.5),
                          legend.title = element_blank())
  
# for (i in occup_list){
#   p <- occup_trend_age %>%
#     filter(occup1 == i) %>%
#     drop_na(female) %>%
#     ggplot(aes(x=age, y=n, group=factor(female), color=factor(female))) +
#     geom_line() + geom_point() +
#     labs(x='Age', y='Number of Respondents', title=paste("Trend Over Time for", i), subtitle="(by age)") +
#     scale_color_manual(values = colors) +
#     theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
#                             plot.subtitle = element_text(hjust = 0.5),
#                             legend.title = element_blank())
#   
#   print(p)
# }
```
  
3. Word cloud for occupations described in `Other`

```{r}
library(tidytext)
library(wordcloud)
library(RColorBrewer)
library(SnowballC)

occs_word <- 
  dat_all %>%
  select(occup1, occs) %>% 
  filter(occup1 == 15, occs != "NULL") %>% 
  unnest_tokens(word, occs) %>%
  mutate(word = wordStem(word)) %>%
  anti_join(stop_words) %>% 
  count(word, sort = TRUE)

wordcloud(words = occs_word$word, freq = occs_word$n, max.words = 50, colors = brewer.pal(8, "Dark2"))
```

## Association between social and structural transitions and occupations

In the following section, for every respondent, only changes in consecutive rounds will be examined. Therefore, a new dataset with only consecutive rounds information is created for the association analysis. A new `include` variable is created to filter the data. For example, if respondent A has data for round 1, 2, 4, 6, and 7, then only data for round 1, 2, 6, and 7 will be selected for further analysis.

```{r}
dat_assoc <- 
  dat_all %>%
  group_by(study_id) %>%
  mutate(visit_prev_change = ifelse((visit - lag(visit, default = visit[1])) == 1, 1, 0)) %>%
  mutate(visit_next_change = ifelse((lead(visit, default = tail(visit,1)) - visit) == 1, 1, 0)) %>%
  mutate(include = ifelse((visit_prev_change + visit_next_change) >= 1, 1, 0)) %>%
  filter(include == 1) %>%
  select(-visit_prev_change, -visit_next_change, -include)
```

1. **Moving (change in `area` in consecutive rounds)**

      ```{r}
      dat_move_occup <-
        dat_assoc %>%
        select(study_id, visit, area, occup1) %>%
        group_by(study_id) %>%
        drop_na(area) %>%
        mutate(visit_prev_change = ifelse((visit - lag(visit, default = visit[1])) == 1, 1, 0)) %>%
        mutate(visit_next_change = ifelse((lead(visit, default = tail(visit,1)) - visit) == 1, 1, 0)) %>%
        mutate(include = ifelse((visit_prev_change + visit_next_change) >= 1, 1, 0)) %>%
        filter(include == 1) %>%
        select(-visit_prev_change, -visit_next_change, -include)

      dat_move_occup <-
        dat_move_occup %>%
        mutate(area_change = ifelse(area != lag(area, default = area[1]), "Moved", "Not Moved")) %>%
        mutate(occup1_change = ifelse(occup1 != lag(occup1, default = occup1[1]), "Changed Occupation", "Did not change occupation")) %>%
        slice(-1) %>%
        ungroup()

      dat_move_occup <-
        dat_move_occup %>% select(area_change, occup1_change)
      ```

    * Let OR = the odds ratio of change occupation for those moved v.s. those who did not move in consecutive rounds
  
    * Hypothesis: $H_0: OR = 1$ v.s. $H_1: OR \neq 1$
  
    * Contingency table
  
      ```{r}
      table_move_occup <- table(dat_move_occup)
      addmargins(table_move_occup)

      mosaicplot(t(table_move_occup), 
                col = c("firebrick", "goldenrod1"), 
                cex.axis = 1, xlab = "Changed Occuaption", ylab = "Moved", main = "")
      ```

    * Use Pearson Chi-squared to test for association
  
      ```{r}
      oddsratio(table_move_occup, method = "wald")
      ```

    * Conclusion: Those who moved in consecutive round has 2.6 times the odds of change occupation as compared to those who did not move (95% CI: 2.06 3.3). Further, we have enough evidence to conclude that this association is statistically significant (p-value = $4.06*10^{-16}$) at 5% LOS.
  
2. **Pregnancy (`everpreg = 1` -> `pregnow = 1` -> `pregnow` change from 0 to 1 in consecutive rounds)**

3. **Drastic change in SES (create a variable called `percentage change in SES` -> when change between consecutive rounds is bigger than 30% (tbd, reference needed)? )**

4. **Have a Child (`livechild` from 0 to 1 in consecutive rounds) **

5. **Marriage (`evermarr 1 =` -> `currmarr = 1` -> `currmarr` change from 0 to 1 in consecutive rounds)**

6. **Marital Dissolution (`evermarr 1 =` -> `currmarr = 0` -> `currmarr` change from 1 to 0 in consecutive rounds)**

## Assess the role in policies like UPE and USE in any shifts in occupations over time


## Variable selection and transformation

## Model fitting
