---
title: "Occupation Trends over Time in AYA"
author: "Amanda(Tianyi) Liu"
date: "13/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height=5, fig.width=8.5,
                      warning=FALSE, message=FALSE, fig.align="center")
```

```{r load_packages}
library(tidyverse)
library(haven)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
library(knitr)
library(magrittr)
library(epitools)
```

## Pre-processing

### Loading Data

```{r load_data}
setwd("/Users/tianyi/Desktop/CUMC/Practicum/rakai_occupation_trend/data")

dat <- read_dta("all_data_original_id_1_19.dta")
dat_part_cleaned <- read_dta("R1_R18_partcleaned_incidence_20190913.dta")

colors <- c("#8d96a3", "#edae49", "#94bee3", "#5ec0b2", "#9fc96c", "#5ec0b2")
```

### Creating full dataset

Only rows from the `all_data_original_id_1_19.dta` dataset will be included in the full dataset.

```{r merge_data}
# `hivrslt`: 1 2 3 7 8 9
hivrslt_dat <- 
  dat_part_cleaned %>% 
  select(study_id, round, hivrslt) %>%
  drop_na(hivrslt)

comm_num_dat <- 
  dat_part_cleaned %>% 
  select(study_id, round, comm_num) %>%
  drop_na(comm_num)

# .y: dat_part_cleaned
# If conflict in data, use data from "all_data_original_id_1_19.dta"

dat_all <- 
  dat %>%
  left_join(hivrslt_dat, by = c("study_id" = "study_id", "round" = "round")) %>%
  mutate(hivrslt = ifelse(is.na(hivrslt.x), hivrslt.y, hivrslt.x)) %>%
  select(-hivrslt.x, -hivrslt.y)

dat_all <-
  dat_all %>%  
  left_join(comm_num_dat, by = c("study_id" = "study_id", "round" = "round")) %>%
  mutate(comm_num = ifelse(is.na(comm_num.x), comm_num.y, comm_num.x)) %>%
  select(-comm_num.x, -comm_num.y)

dat_all %>% relocate(study_id) %>% group_by(study_id)
```

**Check if all requested variables exist**
  
```{r filter_var}
vars <- c("occup1", "occup2", "occupat1", "occupat2", "occs", # outcome
          "female", "ageyrs", "conf_age", "conf_age_flow", # demographics
          "comm_num",
          "radio", "bicycle","car","motorcyc","latrine", # SES
          "electric", "floor", "othfloor", "roof", "walls",
          "everpreg", "pregnow", "livechild", "numchild", # pregnancy
          "evermarr", "currmarr", "polymar", "evermend", # marriage  
          "pabuseyr", "ppushyr", "pfistyr", "pkickyr", # domestic violence
          "pweapyr", "patknyr", "pothvyr",
          "vthrsxpy", "pfocsxpy", "othfsxpy", "othpvyrs",# violence
          "hivrslt",# hiv result
          "occupat11", "occupat21", "occup11", "occup21", "occups1", # partner occupation
          "educate", "educyrs", "school", "finsch", "pregsch", # education
          "movesch", "menasch", "harasch", "bullwsch", "paresch",
          "accomsch", "othsch", "spesch", "addtrain")

dat_all %>% select(all_of(vars))

# "occupat1", "occupat2", "occs",
# "conf_age", "conf_age_flow", visit
# "livechild", "numchild",
# "othpvyrs", "hivrslt",
# "occup11", "occup21", "occups1",
# "addtrain"
```


### Data Cleaning

1. Create `age` variable by merging information from `conf_age_flow`, `conf_age`, `ageyrs`

```{r}
# Prioritization: `conf_age_flow` -> `conf_age` -> `ageyrs`
dat_all <-
  dat_all %>% 
  mutate(age = ifelse(is.na(conf_age_flow), conf_age, conf_age_flow)) %>% 
  mutate(age = ifelse(is.na(age), ageyrs, age))
```

2. Filter by age (15-24 year-old respondents) and generate `age groups` variable (15-17, 18-19, 20-24)

```{r}
dat_all <- 
  dat_all %>%
  filter(15 <= age & age <= 24) %>%
  mutate(age_cat = cut(age, breaks = c(14.5, 17.5, 19.5, 24.5), labels = c(1, 2, 3))) %>%
  mutate(age_cat = labelled(age_cat, c("15-17" = 1, "18-19" = 2, "20-24" = 3)))
```

3. Generate `visit` variable

```{r}
dat_all <- 
  dat_all %>% 
  mutate(visit = str_sub(round, 2, -1)) %>%
  mutate(visit = as.numeric(visit))
```

4. Generate `time period` variable (R1-R9 and R10-R19)

````{r}
dat_all <-
  dat_all %>% 
  mutate(period = cut(visit, breaks = c(0.5, 9.5, 19.5), labels = c(1, 2))) %>%
  mutate(period = labelled(period, c("R1-R9" = 1, "R10-R19" = 2)))
```

5. Generate `area` variable

```{r}
comm_fishing <- c(23, 38, 370, 770, 771, 772, 773, 774, 51, 776)
area_fishing <- rep("fishing", length(comm_fishing))

comm_rural <- c(3, 6, 7, 8, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 25, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 44, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 65, 67, 68, 77, 81, 84, 89, 94, 95, 103, 106, 107, 108, 109, 120, 177, 183, 256, 391, 401, 451, 468, 602, 755, 760, 900, 901)
area_rural <- rep("rural", length(comm_rural))

comm_periurban <- c(1, 2, 4, 5, 9, 22, 24, 26, 40, 45, 46, 74, 754)
area_periurban <- rep("periurban", length(comm_periurban))

area <- data.frame("comm_num" = c(comm_fishing, comm_rural, comm_periurban),
                   "area" = c(area_fishing, area_rural, area_periurban))

dat_all <-
  dat_all %>%
  left_join(area)
```

6. Categorize occupations for respondents (based on R1-18 part cleaned data)

```{r}
# labelling occupations
occup_lab <- c("Agriculture for home use/barter" = 1,
               "Agriculture for selling" = 2,
               "Housework in your own home" = 3,
               "Housekeeper (for relative or employer)" = 4,
               "Home brewing" = 5,
               "Government/clerical/teaching" = 6,
               "Fishing" = 7,
               "Student" = 8,
               "Military/police" = 9,
               "Shopkeeper" = 10,
               "Trading/vending" =	11,
               "Bar worker or owner" = 12,
               "Trucker" =	13,
               "Unemployed" = 14,
               "Other" = 15,
               "No additional occupation" = 88,
               "Medical worker (non-government)" = 16,
               "Casual laborer" =  17,
               "Waitress/Waiter/restaurant owner" = 18,
               "Hair dresser/Salon owner" = 19,
               "Construction (brick maker, builder, porter, painter, roofing)" = 20,
               "Mechanic (automobiles, bicycles, electronics)" = 21,
               "Boda Boda" = 22,
               "Client/Sex worker" = 23,
               "Sports betting, Gambling machine, Ludo" = 24, 
               "Don't know" = 97,
               "Don't know" = 98,
               "No response" = 99)

dat_all$occup1 <- dat_all$occup1 %>% labelled(occup_lab)
dat_all$occup2 <- dat_all$occup2 %>% labelled(occup_lab)

# categorize occupation
occup1_cat <- dat_part_cleaned %>% select(occup1, occup1_cat) %>% unique() %>% arrange(occup1) %>% drop_na(occup1)
occup2_cat <- occup1_cat %>% rename(occup2 = occup1, occup2_cat = occup1_cat)

occup1_mob <- dat_part_cleaned %>% select(occup1, occup1_mob) %>% unique() %>% arrange(occup1) %>% drop_na(occup1)
occup2_mob <- occup1_mob %>% rename(occup2 = occup1, occup2_mob = occup1_mob)

dat_all <- 
  dat_all %>% 
  left_join(occup1_cat, by = ("occup1" = "occup1")) %>%
  left_join(occup1_mob, by = ("occup1" = "occup1"))

dat_all <- dat_all %>% 
  left_join(occup2_cat, by = ("occup2" = "occup2")) %>%
  left_join(occup2_mob, by = ("occup2" = "occup2"))
```

7. Recoding/labelling `hivrslt` variable

```{r}
# `hivrslt`: 1 2 3 7 8 9
hivrslt_lab <- c("Negative" = 1,
                 "Positive" = 2,
                 "Indeterminate" = 3,
                 "Don’t know/Don’t remember" = 7,
                 "NA" = 8,
                 "No Response" = 9)

dat_all$hivrslt <- dat_all$hivrslt %>% labelled(hivrslt_lab)
```

8. Creating `SES` variable

    ```{r}
    setwd("/Users/tianyi/Desktop/CUMC/Practicum/rakai_occupation_trend/data")
    
    ## 1. Select data
    dat_ses <- dat_all %>%
      select(study_id, visit, radio, bicycle, motorcyc, car, latrine, electric, roof, floor, walls)
    
    ## 2. Recode
    dat_ses <- dat_ses %>% 
      mutate(radio_r = ifelse(radio == 1, 1,ifelse(radio %in% c(2,3,5), 0, NA)),
             bicycle_r = ifelse(bicycle == 1, 1,ifelse(bicycle %in% c(2,3,5), 0, NA)),
             car_r = ifelse(car == 1, 1,ifelse(car %in% c(2,3,5), 0, NA)),
             motorcyc_r = ifelse(motorcyc == 1, 1,ifelse(motorcyc %in% c(2,3,5), 0, NA)),
             latrine_r = ifelse(latrine == 1, 1,ifelse(latrine %in% c(2,3,5), 0, NA)),
             electric_r = ifelse(electric == 1, 1,ifelse(electric %in% c(2,3,5), 0, NA)),
             roof_r = ifelse(roof %in% c(1,3), 1,ifelse(roof %in% c(2,4,5), 0, NA)),
             floor_r = ifelse(floor %in% c(2,3), 1,ifelse(floor %in% c(1,5), 0, NA)),
             walls_r = ifelse(walls %in% c(3), 1,ifelse(walls %in% c(1,2,4,5), 0, NA)))
    
    ## 3. Calculate raw SES index
    df_asset_data <- dat_ses %>% 
      select(study_id, visit, radio_r, bicycle_r, motorcyc_r, car_r, latrine_r, electric_r, roof_r, floor_r, walls_r) %>% 
      pivot_longer(cols = radio_r:walls_r, names_to = "variable", values_to = "status") %>%
      arrange(study_id, visit)
    
    df_pca_overall <- readxl::read_xlsx("./PCA_weights.xlsx") %>%
      select(variable, Overall) %>%
      rename(score = Overall) 
    
    df_merge_overall <- left_join(df_asset_data, df_pca_overall, by = 'variable') %>%
      arrange(study_id, visit) %>%
      mutate(SES = status * score) 
    
    df_ovSES_data <- df_merge_overall %>%
      arrange(study_id, visit) %>% 
      group_by(study_id, visit) %>% 
      summarise(SES = sum(SES), na.rm = F) %>%
      ungroup()
    
    df_SES_data <- left_join(df_ovSES_data, dat_ses, by = c('study_id', 'visit')) %>%
      mutate(SES = structure(SES, label = "raw SES score")) %>%
      arrange(study_id, visit) %>%
      select(-na.rm)
    
    ## 4. Create SES z-score and 4-level SES categorical variable
    df_cut_overall <- readxl::read_xlsx("./SES_cutpoints.xlsx") %>%
      select(cutpoints, Overall) %>%
      pivot_wider(names_from = cutpoints, values_from = Overall) %>%
      rename(Q1_zovSES = Q1_stdSES, Q2_zovSES = Q2_stdSES, Q3_zovSES = Q3_stdSES)
    
    df_SES_data <- df_SES_data %>%
      mutate(zovSES = structure((SES - df_cut_overall$mean_SES) / df_cut_overall$sd_SES, label = "Overall standardized SES"), 
             SEScat = case_when(zovSES <= df_cut_overall$Q1_zovSES ~ 0,
                                zovSES > df_cut_overall$Q1_zovSES & zovSES <= df_cut_overall$Q2_zovSES ~ 1,
                                zovSES > df_cut_overall$Q2_zovSES & zovSES <= df_cut_overall$Q3_zovSES ~ 2,
                                zovSES > df_cut_overall$Q3_zovSES ~ 3)) %>%
      #mutate(SEScat = structure(SEScat, label = "zovSES categories"))
      mutate(SEScat = structure(ordered(SEScat, labels = c("lowest", "low-middle", "high-middle", "highest")), label = "zovSES categories"))
    
    ## 5. Merge into large dataset
    df_SES_data <- df_SES_data %>% select(study_id, visit, SES, SEScat)
    dat_all <- dat_all %>% left_join(df_SES_data, by = c("study_id" = "study_id", "visit" = "visit"))
```


## Describe trends over time in AYA occupations

### Visualize general occupation trends

1. Top occupations for each community type

    ```{r}
    top_occup_area <- 
      dat_all %>% 
      select (study_id, visit, area, occup1) %>%
      gather(key, occup, -study_id, -visit, -area) %>%
      as_factor() %>%
      mutate(dummy = "yes") %>%
      spread(occup, dummy) %>%
      gather(job, value,  -study_id, -visit, -area, -key) %>%
      drop_na() %>%
      group_by(area, job) %>%
      summarise_at(vars(value), funs(sum(.=="yes")))
    
    top_occup_area %>% 
      filter(area == "fishing") %>%
      arrange(desc(value)) %>%
      top_n(n=5) %>%
      ggplot(aes(x=factor(job, unique(job)), y=value)) +
      geom_bar(stat="identity", fill="#94bee3", width=0.6) +
      geom_text(aes(label=value), vjust = -1, color = "grey") +
      scale_x_discrete(labels = wrap_format(20)) +
      labs(x='', y='', title = "Top 5 Occupations for Fishing Communities") +
      theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
    
    top_occup_area %>% 
      filter(area == "periurban") %>%
      arrange(desc(value)) %>%
      top_n(n=5) %>%
      ggplot(aes(x=factor(job, unique(job)), y=value)) +
      geom_bar(stat="identity", fill="#94bee3", width=0.6) +
      geom_text(aes(label=value), vjust = -1, color = "grey") +
      scale_x_discrete(labels = wrap_format(20)) +
      labs(x='', y='', title = "Top 5 Occupations for Periurban Communities") +
      theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
    
    top_occup_area %>% 
      filter(area == "rural") %>%
      arrange(desc(value)) %>%
      top_n(n=5) %>%
      ggplot(aes(x=factor(job, unique(job)), y=value, fill)) +
      geom_bar(stat="identity", fill="#94bee3", width=0.6) +
      geom_text(aes(label=value), vjust = -1, color = "grey") +
      scale_x_discrete(labels = wrap_format(20)) +
      labs(x='', y='', title = "Top 5 Occupations for Rural Communities") +
      theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
    ```

2. Top occupations for each gender
  
    ```{r}
    top_occup_gender <- 
      dat_all %>% 
      select (study_id, visit, female, occup1) %>%
      gather(key, occup, -study_id, -visit, -female) %>%
      as_factor() %>%
      mutate(dummy = "yes") %>%
      spread(occup, dummy) %>%
      gather(job, value,  -study_id, -visit, -female, -key) %>%
      drop_na() %>%
      group_by(female, job) %>%
      summarise_at(vars(value), funs(sum(.=="yes")))
    
    top_occup_gender %>% 
      filter(female == "Male") %>%
      arrange(desc(value)) %>%
      top_n(n=5) %>%
      ggplot(aes(x=factor(job, unique(job)), y=value)) +
      geom_bar(stat="identity", fill="#94bee3", width=0.6) +
      geom_text(aes(label=value), vjust = -1, color = "grey") +
      scale_x_discrete(labels = wrap_format(20)) +
      labs(x='', y='', title = "Top 5 Occupations for Male") +
      theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
    
    top_occup_gender %>% 
      filter(female == "Female") %>%
      arrange(desc(value)) %>%
      top_n(n=5) %>%
      ggplot(aes(x=factor(job, unique(job)), y=value)) +
      geom_bar(stat="identity", fill="#94bee3", width=0.6) +
      geom_text(aes(label=value), vjust = -1, color = "grey") +
      scale_x_discrete(labels = wrap_format(20)) +
      labs(x='', y='', title = "Top 5 Occupations for Female") +
      theme_minimal() + 
      theme(plot.title = element_text(hjust = 0.5))
    ```

3. Top occupations for each age group

    ```{r}
    top_occup_agecat <- 
      dat_all %>% 
      select (study_id, visit, female, age_cat, occup1) %>%
      gather(key, occup, -study_id, -visit, -age_cat, -female) %>%
      as_factor() %>%
      mutate(dummy = "yes") %>%
      spread(occup, dummy) %>%
      gather(job, value,  -study_id, -visit, -age_cat, -key, -female) %>%
      drop_na() %>%
      group_by(age_cat, job, female) %>%
      summarise_at(vars(value), funs(sum(.=="yes"))) %>%
      mutate(frequency = sum(value))
      
    for (i in c("15-17", "18-19", "20-24")){
      p <- top_occup_agecat %>% 
        filter(age_cat == i) %>%
        arrange(desc(frequency)) %>%
        head(10) %>%
        ggplot(aes(x = factor(job, unique(job)), y = value, fill = female, label = value)) +
        geom_bar(stat = "identity")+
        geom_text(size = 3, position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values=colors) +
        scale_x_discrete(labels = wrap_format(15)) +
        labs(x='', y='', title = paste("Top Occupations for Respondents Aged", i)) +
        theme_minimal() + 
        theme(plot.title = element_text(hjust = 0.5),
              legend.title = element_blank())
      print(p)
    }
    ```

It can be observed from above analysis that the top occupations for AYA include `Student`, `Agriculture for home use/barter`, `Housework in your own home`, `Agriculture for selling`, `Government/clerical/teaching`, `Trading/Vending` and `Other` (in addition to one community-specific occupation `Fishing`). Therefore, following analysis will be mainly focused on these occupations.

### Trends over time in AYA occupations

1. Trend by `visit`
  
    ```{r}
    # Student 8
    # Agriculture for home use/barter 1
    # Housework in your own home 3
    # Agriculture for selling 2
    # Government/clerical/teaching 6
    # Trading/Vending 11
    # Other 15
    # Fishing 7
    
    occup_list <- c("Student", 
                    "Agriculture for home use/barter", 
                    "Housework in your own home", 
                    "Agriculture for selling", 
                    "Government/clerical/teaching", 
                    "Trading/vending", 
                    "Other", 
                    "Fishing")
    ```

    ```{r}
    occup_trend_visit <- dat_all %>% 
      select(study_id, visit, area, female, age, age_cat, occup1, occup1_cat, occup1_mob) %>%
      filter(occup1 %in% c(1, 2, 3, 6, 7, 8, 11, 15)) %>% 
      group_by(occup1, visit, female) %>%
      count(occup1) %>%
      as_factor()
    
    occup_trend_visit %>%
      drop_na(female) %>%
      group_by(occup1) %>%
      ggplot(aes(x=visit, y=n, group=factor(female), color=factor(female))) +
      geom_line() + geom_point() + facet_wrap(~occup1) +
      labs(x='Visit', y='Number of Respondents', title="Trend Over Time for Occupations", subtitle="by visit") +
      scale_color_manual(values = colors) +
      theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
                              plot.subtitle = element_text(hjust = 0.5),
                              legend.title = element_blank())
    
    # for (i in occup_list){
    #   p <- occup_trend_visit %>%
    #     filter(occup1 == i) %>%
    #     drop_na(female) %>%
    #     ggplot(aes(x=visit, y=n, group=factor(female), color=factor(female))) +
    #     geom_line() + geom_point()+
    #     labs(x='Visit', y='Number of Respondents', title = paste("Trend Over Time for", i), subtitle = "(by visit)") +
    #     scale_color_manual(values = colors) +
    #     theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
    #                             plot.subtitle = element_text(hjust = 0.5),
    #                             legend.title = element_blank())
    #   print(p)
    # }
    ```
  
2. Trend by `age`
  
    ```{r}
    occup_trend_age <- dat_all %>% 
      select(study_id, visit, area, female, age, age_cat, occup1, occup1_cat, occup1_mob) %>%
      filter(occup1 %in% c(1, 2, 3, 6, 7, 8, 11, 15)) %>% 
      group_by(occup1, age, female) %>%
      count(occup1) %>%
      as_factor()
    
    occup_trend_age %>%
      drop_na(female) %>%
      group_by(occup1) %>%
      ggplot(aes(x=age, y=n, group=factor(female), color=factor(female))) +
      geom_line() + geom_point() + facet_wrap(~occup1) +
      labs(x='Age', y='Number of Respondents', title="Trend Over Time for Occupations", subtitle="(by age)") +
      scale_color_manual(values = colors) +
      theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
                              plot.subtitle = element_text(hjust = 0.5),
                              legend.title = element_blank())
      
    # for (i in occup_list){
    #   p <- occup_trend_age %>%
    #     filter(occup1 == i) %>%
    #     drop_na(female) %>%
    #     ggplot(aes(x=age, y=n, group=factor(female), color=factor(female))) +
    #     geom_line() + geom_point() +
    #     labs(x='Age', y='Number of Respondents', title=paste("Trend Over Time for", i), subtitle="(by age)") +
    #     scale_color_manual(values = colors) +
    #     theme_minimal() + theme(plot.title = element_text(hjust = 0.5),
    #                             plot.subtitle = element_text(hjust = 0.5),
    #                             legend.title = element_blank())
    #   
    #   print(p)
    # }
    ```
  
3. Word cloud for occupations described in `Other`

    ```{r}
    library(tidytext)
    library(wordcloud)
    library(RColorBrewer)
    library(SnowballC)
    
    occs_word <- 
      dat_all %>%
      select(occup1, occs) %>% 
      filter(occup1 == 15, occs != "NULL") %>% 
      unnest_tokens(word, occs) %>%
      mutate(word = wordStem(word)) %>%
      anti_join(stop_words) %>% 
      count(word, sort = TRUE)
    
    wordcloud(words = occs_word$word, freq = occs_word$n, max.words = 50, colors = brewer.pal(8, "Dark2"))
    ```

## Association between social and structural transitions and occupations

I choose to examine the following social and structural transitions and their impacts on occupation (focusing on `occup1`):

  1. Moving (from one area to another)

  2. Initiation of child bearing -> pregnancy (from no to yes)

  3. Having child (from no to yes)
  
  4. Change in SES

  5. Marriage

  6. Marital dissolution
  
In addition, in the following section, for every respondent, I choose to only analyse changes in consecutive rounds. Therefore, a new dataset `dat_assoc` with only information from consecutive rounds is created for the association analysis. 

I will first select the variables that will be used and cross reference with different columns to verify their validity. Missing values will be fill in if possible. Then, a new `include` variable is created to filter the data. For example, if respondent A has data for round 1, 2, 4, 6, and 7, then only data for round 1, 2, 6, and 7 will be selected for further analysis.

### Data Recoding and Verification

1. Select variables needed, drop respondent with missing values for features that cannot be filled in using other features

```{r}
dat_assoc <-
  dat_all %>%
  select(study_id, visit, occup1, area, female, everpreg, pregnow, SES, SEScat, livechild, numchild, evermarr, currmarr) %>%
  drop_na(study_id, visit, occup1, area)
```

2. `numchild` - female only + male for Rn15 & 16

```{r echo=FALSE}
numchild_val <- c('NA', 0:8, 98, 99)
numchild_label <- c("Missing", "None", rep("Number of child", 7) , "Skipped (no livechild or never been pregnant)", "DK", "NR")
numchild_maniplation <- c("Replace NA with 99 (NR)", rep("", 8), "Replace 8 with 0 (None)", "", "")

data.frame(numchild = numchild_val, Label = numchild_label, Manipulation = numchild_maniplation) %>% 
  kable(style = "html", caption = "numchild") %>% 
  kable_styling("striped", position = "center") %>%
  scroll_box(height = "200px")
```

```{r}
dat_assoc <-
  dat_assoc %>% 
  mutate(numchild = ifelse(is.na(numchild), 99, numchild)) %>% 
  mutate(numchild = ifelse(numchild == 8, 0, numchild))
```

3. `livechild` - 0 (male); 1 (female) for Rnd 2, 3, 4, 15, 16, 18, 19

```{r echo=FALSE}
livechild_val <- dat_assoc %>% select(livechild) %>% unique() %>% arrange(livechild) %>% as.list()
livechild_label <- c("Only one person has livechild=0 (numchild=98 DK; evergpreg=1; pregnow=1)", 
                     "Yes", 
                     "No", 
                     "Skipped (never been pregnant)", 
                     "People with livechild=9 has numchild=99 (NR)", "Missing")
livechild_manipulation <- c("Replacce with 8 (NR)", 
                            "", 
                            "", 
                            "", 
                            "Replace with 8 (NR)", 
                            "Replace with 8 (NR)")

data.frame(Value = livechild_val, Meaning = livechild_label, Manipulation = livechild_manipulation) %>% 
  kable(style = "html", caption = "livechild") %>% 
  kable_styling("striped", position = "center") %>%
  scroll_box(height = "200px")
```

```{r}
dat_assoc <-
  dat_assoc %>% 
  mutate(livechild = ifelse(livechild == 0, 8, livechild)) %>%
  mutate(livechild = ifelse(livechild == 9, 8, livechild)) %>%
  mutate(livechild = ifelse(is.na(livechild), 8, livechild))

# cross checking livechild v.s. numchild
# livechild == 2 -> numchild = 0 | 99
dat_assoc %>% filter(livechild == 2) %>% select(numchild) %>% unique()

# if livechild == 2 & numchild == 2, then livechild = 1
# if livechild == 2 & numchild == 98, then numchild = 99
dat_assoc <-
  dat_assoc %>% 
  mutate(livechild = ifelse(livechild == 2 & numchild == 2, 1, livechild)) %>%
  mutate(numchild = ifelse(livechild == 2 & numchild == 98, 99, numchild))
```

4. `pregnow` - female only

```{r echo=FALSE}
pregnow_val <- c(1, 2, 3, 7, 8, NA)
pregnow_label <- c("Yes", "No", "Uncertain (Rnd 4)", "DK", "N/A", "NA")
pregnow_manipulation <- c("", "", "Replace with 7 (DK)", "", "Label as NR", "Replace with 8")

data.frame(pregnow = pregnow_val, Label = pregnow_label, Manipulation = pregnow_manipulation) %>% 
  kable(style = "html", caption = "pregnow") %>% 
  kable_styling("striped", position = "center") %>%
  scroll_box(height = "200px")
```

```{r}
dat_assoc <-
  dat_assoc %>% 
  mutate(pregnow = ifelse(pregnow == 3, 7, pregnow)) %>%
  mutate(pregnow = ifelse(is.na(pregnow), 8, pregnow))
```

5. `everpreg` - female only

```{r echo=FALSE}
everpreg_val <- c(1, 2, 7, 8, NA)
everpreg_label <- c("Yes", "No", "DK", "N/A", "NA")
pregnow_manipulation <- c("", "", "", "Label as NR", "Replace with 8")

data.frame(everpreg = everpreg_val, Label = everpreg_label, Manipulation = pregnow_manipulation) %>% 
  kable(style = "html", caption = "everpreg") %>% 
  kable_styling("striped", position = "center") %>%
  scroll_box(height = "200px")
```

```{r}
dat_assoc <-
  dat_assoc %>% 
  mutate(everpreg = ifelse(is.na(everpreg), 8, everpreg))

# cross checking everpreg v.s. pregnow
# if pregnow == 1 then everpreg = 1
dat_assoc %>% filter(pregnow == 1) %>% select(everpreg) %>% unique()

# pregnow == 1 & everpreg == 8 -> everpreg = 1
dat_assoc <- 
  dat_assoc %>% 
  mutate(everpreg  = ifelse((pregnow == 1 & everpreg == 8), 1, everpreg))

# corss checking everpreg v.s. numchild
# if numchild %in% c(1:7) then everpreg = 1 (when female = 1)
dat_assoc %>% filter(numchild %in% c(1:7), female == 1) %>% select(everpreg) %>% unique()
```

6. `female`: 0 (male), 1 (female)

```{r echo=FALSE}
female_val <- c(0, 1, NA)
female_label <- c("Male", "Female", "NA")
female_manipulation <- c("", "", "Filled by comparing everpreg and pregnow")

data.frame(female = female_val, Label = female_label, Manipulation = female_manipulation) %>% 
  kable(style = "html", caption = "female") %>% 
  kable_styling("striped", position = "center") %>%
  scroll_box(height = "200px")
```

```{r}
dat_assoc %>% filter(is.na(female))

# Gender of H131540 cannot be determined
dat_assoc <- 
  dat_assoc %>% 
  mutate(female = ifelse(study_id=="H131435", 1, female)) %>% 
  drop_na(female)

# cross checking everpreg v.s. pregnow v.s. female
# if everpreg = 1 | pregnow = 1 then female = 1
dat_assoc %>% filter(everpreg == 1 | pregnow == 1) %>% select(female) %>% unique()

# there are respodents whose gender does not correspond to pregnancy status
dat_assoc %>% filter(everpreg == 1 | pregnow == 1, female == 0)

# B020838 and G005620
dat_all %>% filter(study_id == "B020838" | study_id == "G005620") %>%   
  select(study_id, visit, female, everpreg, pregnow, livechild, numchild)

# B020838 is recorded as a male in other visits
# pregnow = 1 in visit 2 can be considered as a data entry error
dat_assoc %>% filter(study_id == "B020838")

dat_assoc <-
  dat_assoc %>% 
  mutate(pregnow = ifelse(study_id == "B020838", 8, pregnow)) %>%
  mutate(everpreg = ifelse(study_id == "B020838", 8, everpreg))

# G005620 has record for everpreg and pregnow, suggesting she is a female 
# since only female get asked about their pregnancy status
# female = 0 can be considered as a data entry error
dat_assoc %>% filter(study_id == "G005620")

dat_assoc <-
  dat_assoc %>% 
  mutate(female = ifelse(study_id == "G005620", 1, female))
```

7. `evermarr`

```{r}
evermarr_val <- c(1, 2, 8, NA)
evermarr_label <- c("Yes", "No", "N/A", "NA")
evermarr_manipulation <- c("", "", "Label as NR", "Replace with 8")

data.frame(evermarr = evermarr_val, Label = evermarr_label, Manipulation = evermarr_manipulation) %>% 
  kable(style = "html", caption = "evermarr") %>% 
  kable_styling("striped", position = "center") %>%
  scroll_box(height = "200px")
```

```{r}
dat_assoc <-
  dat_assoc %>% 
  mutate(evermarr = ifelse(is.na(evermarr), 8, evermarr))
```

8. `currmarr`

```{r}
currmarr_val <- c(0, 1, 2, 8, 9, NA)
currmarr_label <- c("0", "Currently married", "Previously married", "Never been married", "9", "NA")
currmarr_manipulation <- c("Replace with 9", "", "", "", "Label as NR", "Replace with 9")

data.frame(currmarr = currmarr_val, Label = currmarr_label, Manipulation = currmarr_manipulation) %>%
  kable(style = "html", caption = "currmarr") %>% 
  kable_styling("striped", position = "center") %>%
  scroll_box(height = "200px")
```

```{r}
dat_assoc<-
  dat_assoc %>% 
  mutate(currmarr = ifelse(currmarr == 0, 9, currmarr)) %>%
  mutate(currmarr = ifelse(is.na(currmarr), 9, currmarr)) %>%
  mutate(currmarr = labelled(currmarr, c("Currently married" = 1,
                                         "Previously married" = 2,
                                         "Never been married" = 8,
                                         "NR" = 9)))

# cross checking evermarr v.s. currmarr
# if currmarr = 1 | 2 then evermarr = 1
dat_assoc %>% filter(currmarr == 1 | currmarr == 2) %>% select(evermarr) %>% unique()
dat_assoc %>% filter(currmarr == 1 | currmarr == 2, evermarr == 8)
### QUESTION
```

9. Labeling all categorical variables

```{r}
dat_assoc <-
  dat_assoc %>% 
  mutate(numchild = labelled(numchild, c("None" = 0, "DK" = 98, "NR" = 99))) %>%
  mutate(livechild = labelled(livechild, c("Yes" = 1, "No" = 2, "NR" = 8))) %>%
  mutate(pregnow = labelled(pregnow, c("Yes" = 1, "No" = 2, "DK" = 7, "NR" = 8))) %>%
  mutate(everpreg = labelled(everpreg, c("Yes" = 1, "No" = 2, "DK" = 7, "NR" = 8))) %>%
  mutate(female = labelled(female, c("Female" = 1, "Male" = 0))) %>%
  mutate(evermarr = labelled(evermarr, c("Yes" = 1, "No" = 2, "NR" = 8))) 
# %>% mutate(currmarr = labelled(currmarr, c()))
```

10. Filter data by consecutive rounds

```{r}
dat_assoc <-
  dat_assoc %>%
  group_by(study_id) %>%
  mutate(visit_prev_change = ifelse((visit - lag(visit, default = visit[1])) == 1, 1, 0)) %>%
  mutate(visit_next_change = ifelse((lead(visit, default = tail(visit,1)) - visit) == 1, 1, 0)) %>%
  mutate(include = ifelse((visit_prev_change + visit_next_change) >= 1, 1, 0)) %>%
  filter(include == 1)
```

